---
title: "Generate local CARWatch example data"
output: html_document
---

Create deterministic raw logs, a manual diary, an editable issue report, and
position-indexed cortisol measurements. The generator writes ordinary input
artifacts and validates the same two-pass workflow used for real studies.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(carwatch)

study_dir <- file.path(tempdir(), "carwatch-gallery-example-data")
```

```{r generate}
generate_synthetic_study_data(
  study_dir,
  n_participants = 4,
  non_compliant_sample_ratio = 0.10,
  missing_awakening_time_ratio = 0.05,
  missing_sampling_time_ratio = 0.10,
  random_state = 42,
  create_cortisol_data = TRUE,
  overwrite = TRUE
)

list.files(study_dir, recursive = TRUE)
```

```{r inspect}
read_manual_diary(file.path(study_dir, "manual_diary.csv"))
read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
readr::read_csv(file.path(study_dir, "cortisol.csv"), show_col_types = FALSE)
```

Set `study_dir` to a controlled project path to retain the generated files.
`overwrite = TRUE` is required before an existing non-empty target is replaced.
