---
title: "Resolve conversion issues through a CSV report"
output: html_document
---

CARWatch conversion is a two-pass process. The first pass creates an advisory
report. Only a report supplied to the second pass executes decisions.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(carwatch)

study_dir <- file.path(tempdir(), "carwatch-gallery-spreadsheet-decisions")
generate_synthetic_study_data(
  study_dir,
  n_participants = 3,
  missing_awakening_time_ratio = 0.05,
  missing_sampling_time_ratio = 0.10,
  random_state = 42,
  overwrite = TRUE,
  validate = FALSE
)

folders <- list.dirs(file.path(study_dir, "logs"), recursive = FALSE, full.names = TRUE)
participant_dirs <- stats::setNames(folders, basename(folders))
raw_logs <- read_raw_logs_from_participant_dirs(participant_dirs)
```

## Export the advisory report

```{r advisory}
advisory <- suppressWarnings(convert_raw_logs(
  raw_logs,
  errors = "warn",
  create_report = TRUE
))

report_path <- file.path(study_dir, "conversion_issues_for_review.csv")
write_conversion_report(advisory$report, report_path)
advisory$report$issues[, c("issue_id", "code", "proposed_action", "resolution_status")]
```

Edit only `user_decision` and `user_decision_value`. Do not alter `issue_id` or
the context columns. The generated study also contains a reviewed report so the
example can execute without manual spreadsheet interaction.

## Apply submitted decisions

```{r submitted}
decisions <- read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))

final <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  create_report = TRUE,
  issue_decisions = decisions,
  manual_diary = manual_diary
)

final$report$issues[, c("issue_id", "code", "resolution_status")]
head(as_sample_events(final$results))
```
