---
title: "Resolve conversion issues interactively"
output: html_document
---

The Shiny/DT editor is the R-native alternative to spreadsheet review. The
issue table is on the left and decision controls are on the right. It restricts
decisions by issue code. **Refresh remaining issues** reruns conversion from the
original logs, and `Done` returns the complete validated decision history.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(carwatch)

if (!requireNamespace("shiny", quietly = TRUE) ||
    !requireNamespace("DT", quietly = TRUE)) {
  stop("Install the optional packages with install.packages(c('shiny', 'DT')).")
}

study_dir <- file.path(tempdir(), "carwatch-gallery-interactive-decisions")
generate_synthetic_study_data(
  study_dir,
  n_participants = 3,
  missing_awakening_time_ratio = 0.05,
  missing_sampling_time_ratio = 0.10,
  random_state = 42,
  overwrite = TRUE,
  validate = FALSE
)

folders <- list.dirs(file.path(study_dir, "logs"), recursive = FALSE, full.names = TRUE)
participant_dirs <- stats::setNames(folders, basename(folders))
raw_logs <- read_raw_logs_from_participant_dirs(participant_dirs)
```

```{r prepare-app}
advisory <- suppressWarnings(convert_raw_logs(
  raw_logs,
  errors = "warn",
  create_report = TRUE
))

manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))
app <- conversion_report_editor(
  advisory$report,
  raw_logs = raw_logs,
  manual_diary = manual_diary,
  launch = FALSE
)
class(app)
```

Run the following in an interactive R session. Decisions are applied only by
the subsequent strict conversion.

```{r launch-app, eval=FALSE}
decisions <- conversion_report_editor(
  advisory$report,
  raw_logs = raw_logs,
  manual_diary = manual_diary
)

study_results <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  issue_decisions = decisions,
  manual_diary = manual_diary
)
```
