---
title: "CARWatch raw-log processing"
output:
  html_document:
    toc: true
    toc_float: true
---

This walkthrough creates a local example study, imports the app logs, reviews
the first conversion report, applies the generated decisions and manual diary,
then writes complete Study Results.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
#library(carwatch)
pkgload::load_all("..", reset = TRUE)

# Use a disposable directory. Set this to a project data directory for a real
# study, then keep the generated report and final results with the study files.
study_dir <- file.path(tempdir(), "carwatch-r-log-example")
```

## Create local example inputs

`generate_synthetic_study_data()` creates raw app exports, a manual diary,
submitted decisions, and position-indexed cortisol measurements. It does not
modify an existing directory unless `overwrite = TRUE` is explicit.

```{r generate}
generate_synthetic_study_data(
  study_dir,
  n_participants = 4,
  random_state = 42,
  missing_sampling_time_ratio = 0.10,
  create_cortisol_data = TRUE,
  overwrite = TRUE
)

list.files(study_dir, recursive = TRUE)
```

## Import raw logs and check the imported files

For real studies, replace `study_dir` with one folder per participant. The
participant identifier comes from the folder mapping you provide. CARWatch does
not try to derive it from a tube ID or file name.

```{r import}
participant_folders <- list.dirs(file.path(study_dir, "logs"),
  recursive = FALSE, full.names = TRUE
)
participant_dirs <- stats::setNames(
  participant_folders,
  basename(participant_folders)
)

imported <- read_raw_logs_from_participant_dirs(
  participant_dirs,
  create_report = TRUE
)
raw_logs <- imported$raw_logs
source_audit <- imported$source_audit

summarize_source_audit(source_audit)
```

## First pass: advisory conversion report

The first pass lists issues but does not apply its suggested actions. The app
logs remain unchanged. Export this table for spreadsheet review in a real study
and retain its identifying and context columns.

```{r advisory}
advisory <- convert_raw_logs(
  raw_logs,
  errors = "warn",
  create_report = TRUE
)

advisory$report$summary
advisory$report$issues

report_path <- file.path(study_dir, "conversion_issues_advisory.csv")
readr::write_csv(advisory$report$issues, report_path, na = "")
report_path
```

## Second pass: submitted decisions and manual diary

The synthetic data include a ready-to-submit report. `read_conversion_report()`
validates decision values and stable IDs. In a real study, edit only
`user_decision` and `user_decision_value`, then read the edited CSV here.

```{r final-conversion}
decisions <- read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))

final <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  create_report = TRUE,
  issue_decisions = decisions,
  manual_diary = manual_diary
)
study_results <- final$results

final$report$summary
final$report$issues
```

## Inspect and save complete results

Keep `study_results` as the complete result object. `as_study_days()` and
`as_sample_events()` create convenient tables for inspection.

```{r inspect-save}
study_days <- as_study_days(study_results)
sample_events <- as_sample_events(study_results)

head(study_days)
head(sample_events)

results_path <- file.path(study_dir, "study_results.csv")
write_study_results(study_results, results_path)

# The complete CSV preserves the information needed to reload the result later.
restored <- read_study_results(results_path)
identical(study_results, restored)
```

## Quality control

```{r quality-control, fig.width=9, fig.height=5}
plot_sampling_timeline(study_results, participant = names(participant_dirs)[[1]], day = "D1")
plot_compliance_overview(study_results)
plot_timing_deviation(study_results)
```

The next walkthrough starts from `study_results.csv` and merges the generated
laboratory data.
