---
title: "CARWatch saliva merge and analysis"
output:
  html_document:
    toc: true
    toc_float: true
---

This walkthrough creates local example inputs, completes the conversion,
merges cortisol measurements by sample position, computes response features,
and produces static plots.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
#library(carwatch)
pkgload::load_all("..", reset = TRUE)

study_dir <- file.path(tempdir(), "carwatch-r-saliva-example")
```

## Build complete Study Results

Merging and feature calculation require the complete result object, not the
compact display table created with `simple = TRUE`.

```{r conversion}
generate_synthetic_study_data(
  study_dir,
  n_participants = 4,
  random_state = 42,
  missing_sampling_time_ratio = 0.10,
  create_cortisol_data = TRUE,
  overwrite = TRUE
)

folders <- list.dirs(file.path(study_dir, "logs"), recursive = FALSE, full.names = TRUE)
participant_dirs <- stats::setNames(folders, basename(folders))
raw_logs <- read_raw_logs_from_participant_dirs(participant_dirs)
decisions <- read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))

study_results <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  issue_decisions = decisions,
  manual_diary = manual_diary
)
```

## Merge laboratory data by sample position

The generated cortisol file uses sample positions. CARWatch gets these from the
study setup; it does not try to infer them from the spelling of a tube ID.

```{r merge}
cortisol <- readr::read_csv(
  file.path(study_dir, "cortisol.csv"),
  show_col_types = FALSE
)

merged_results <- merge_saliva(
  study_results,
  cortisol,
  match_on = "position"
)

head(as_sample_events(merged_results))
```

For a laboratory file keyed by physical ID instead, use `read_saliva()` and
`match_on = "sample"`. CARWatch uses `recorded_sample` to correct documented
swaps when `correct_swaps = TRUE`.

## Restrict to compliant observations and compute features

```{r features}
analysis_results <- drop_non_compliant_samples(merged_results)
summarize_compliance(merged_results)
find_sampling_anomalies(merged_results)

cortisol_features <- compute_features_from_carwatch(
  analysis_results,
  saliva_type = "cortisol"
)
cortisol_features
```

## Plot timing and cortisol response

```{r plots, fig.width=9, fig.height=5}
plot_saliva_curve(merged_results, value = "cortisol")
plot_timing_deviation(merged_results)
```

Save complete merged results and features as ordinary analysis artifacts.

```{r save}
write_study_results(merged_results, file.path(study_dir, "study_results_cortisol.csv"))
readr::write_csv(cortisol_features, file.path(study_dir, "cortisol_features.csv"), na = "")
```
