---
title: "CARWatch plotting"
output:
  html_document:
    toc: true
    toc_float: true
---

This walkthrough reproduces the Python plotting notebook with R-native
`ggplot2` objects. It builds complete Study Results, merges deterministic
cortisol measurements, and creates the four CARWatch quality-control plots.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(carwatch)

study_dir <- file.path(tempdir(), "carwatch-r-plotting-example")
```

## Prepare complete Study Results

```{r prepare}
generate_synthetic_study_data(
  study_dir,
  n_participants = 4,
  non_compliant_sample_ratio = 0.15,
  missing_awakening_time_ratio = 0,
  missing_sampling_time_ratio = 0.05,
  random_state = 42,
  create_cortisol_data = TRUE,
  overwrite = TRUE
)

folders <- list.dirs(file.path(study_dir, "logs"), recursive = FALSE, full.names = TRUE)
participant_dirs <- stats::setNames(folders, basename(folders))
raw_logs <- read_raw_logs_from_participant_dirs(participant_dirs)
decisions <- read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))

study_results <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  issue_decisions = decisions,
  manual_diary = manual_diary
)

cortisol <- readr::read_csv(
  file.path(study_dir, "cortisol.csv"),
  show_col_types = FALSE
)
merged_results <- merge_saliva(study_results, cortisol, match_on = "position")
```

## Participant-day sampling timeline

Expected registered times are open markers. Recorded times are coloured by
compliance and shaped by their source.

```{r timeline, fig.width=9, fig.height=5}
plot_sampling_timeline(study_results, participant = names(participant_dirs)[[1]], day = "D1")
```

## Cohort compliance

```{r compliance-proportion, fig.width=8, fig.height=5}
plot_compliance_overview(study_results, view = "proportion")
```

```{r compliance-heatmap, fig.width=8, fig.height=5}
plot_compliance_overview(study_results, view = "heatmap")
```

## Timing deviations

```{r timing-deviation, fig.width=8, fig.height=5}
plot_timing_deviation(study_results)
```

## Cortisol response

The saliva curve uses observed minutes since awakening and preserves the
participant-day curves behind the cohort mean.

```{r saliva-curve, fig.width=8, fig.height=5}
plot_saliva_curve(merged_results, value = "cortisol")
```
