---
title: "Interactive CARWatch log processing with synthetic data"
output:
  html_document:
    toc: true
    toc_float: true
---

This walkthrough creates an example study, builds a first conversion report,
and prepares the Shiny conversion editor and participant-day timeline.
Rendering does not open the apps; run the final calls interactively to open
each one.

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
#library(carwatch)
pkgload::load_all("..", reset = TRUE)

if (!requireNamespace("shiny", quietly = TRUE) ||
    !requireNamespace("DT", quietly = TRUE)) {
  stop("Install the optional packages with install.packages(c('shiny', 'DT')).")
}

study_dir <- file.path(tempdir(), "carwatch-r-interactive-example")
```

## Generate and import a study

```{r generate-import}
generate_synthetic_study_data(
  study_dir,
  n_participants = 3,
  non_compliant_sample_ratio = 0.10,
  missing_awakening_time_ratio = 0.05,
  missing_sampling_time_ratio = 0.10,
  random_state = 42,
  overwrite = TRUE,
  validate = FALSE
)

folders <- list.dirs(file.path(study_dir, "logs"), recursive = FALSE, full.names = TRUE)
participant_dirs <- stats::setNames(folders, basename(folders))
raw_logs <- read_raw_logs_from_participant_dirs(participant_dirs)
manual_diary <- read_manual_diary(file.path(study_dir, "manual_diary.csv"))
```

## Prepare the conversion-report editor

The first pass is advisory. Constructing an editor never modifies `raw_logs`.
The issue table is on the left and its decision controls are on the right. The
app validates decisions with the same rules as `convert_raw_logs()`. Apply a
decision, then select **Refresh remaining issues** to rerun conversion from the
original events and replace the table with the unresolved queue.

```{r report-editor}
advisory <- suppressWarnings(convert_raw_logs(
  raw_logs,
  errors = "warn",
  create_report = TRUE
))

report_app <- conversion_report_editor(
  advisory$report,
  raw_logs = raw_logs,
  manual_diary = manual_diary,
  launch = FALSE
)
class(report_app)
```

In an interactive R session, launch the editor and retain the returned decision
table:

```{r launch-editor, eval=FALSE}
decisions <- conversion_report_editor(
  advisory$report,
  raw_logs = raw_logs,
  manual_diary = manual_diary
)
write_conversion_report(decisions, file.path(study_dir, "conversion_issues.csv"))

final_results <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  issue_decisions = decisions,
  manual_diary = manual_diary
)
```

## Prepare the interactive timeline

The generated submitted decisions can be used to create final results during a
noninteractive render. `launch = FALSE` returns the Shiny app object.

```{r timeline-app}
submitted <- read_conversion_report(file.path(study_dir, "issue_decisions.csv"))
study_results <- convert_raw_logs(
  raw_logs,
  errors = "raise",
  issue_decisions = submitted,
  manual_diary = manual_diary
)

timeline_app <- interactive_sampling_timeline(study_results, launch = FALSE)
class(timeline_app)
```

```{r launch-timeline, eval=FALSE}
interactive_sampling_timeline(study_results)
```
